MA_Results

### 2024-02-23 Markdown/Manuscript/Child_RMDs/MS_Imp_Example.Rmd
nearly done on model

<!-- Although we are principally interested in using CHEMs to answer policy questions relating to the mental health of young people in Australia, we want to facilitate CHEM transferability to other jurisdictions.  -->

Our CHEMs are being derived from and applied to real data (which can be empirical, simulated or assumption, so long as it is appropriate for use in analysis intended to inform decision-making) from Australia. To help demonstrate the potential use of CHEMs in other decision contexts, we also create toy datasets. Data created for illustration purposes is prominently labelled as not for use in decision-analysis.

## Case study: health and its value
We have previously described a study [@Hamilton2021.07.07.21260129] to develop utility mapping models for use in samples of young people presenting to primary mental health services. The ready4 software framework was used in that study to develop CHEM modules, supply those modules with data and implement modelling analyses, creating the following artefacts:

@@

We created a checklist (Table \@ref(tab:checktb)) that we used to subjectively assess these study outputs against <!-- Edit_start -->explicit criteria for assessing transparent, reusable and updatable CHEMs that we have previously developed (add REF) <!-- Edit_end -->. For each criterion, we provided a global assessment of whether it was met using the responses “yes”, “no” or “partial”.  We believe our utility mapping study CHEMs have satisfactorily met five of the six criteria (T1, T2, R1, R2 and U1) and have partially met one criterion (U2). The main shortcomings that we identified when applying the assessment criteria was that we have yet to adequately implement unit testing of the R libraries authored as part of this study.

>>>>

<!-- Although we are principally interested in using CHEMs to answer policy questions relating to the mental health of young people in Australia, we want to facilitate CHEM transferability to other jurisdictions.  -->
Our early use of the ready4 framework has focused on developing readyforwhatsnext modules for constructing, sharing and using utility mapping models in youth mental health.

## Model user requirements
The initial model user requirements (MURs) that we specified for initial readyforwhatsnext modules we developed for utility mapping were:

MUR 1) *Variable validation tools* that: (i) define the allowable range (minimum and maximum) and numeric class (integer or double precision) associated with different psychological, functional and health utility summary measures appropriate for use in youth mental health samples; (ii) provide an informative error message that halts an analysis or reporting program's execution should impermissible values be assigned to each measure.

MUR 2) *Dataset description tools* that: (i) attach metadata to a human records dataset that specifies the unique person identifier, group assignment and data collection round variables; and (ii) generate tabular and graphical summaries of dataset descriptive statistics.

MUR 3) *Multi-attribute instrument tools* that: (i) attaches structured metadata about an instrument (e.g. name, version, country, items, domains, parameter values for scoring algorithms) to a human records dataset; (ii) applies a pre-written (for AQol-6D and EQ-5D instruments) or user-supplied instrument scoring function to a human records dataset; and (iii) generates descriptive plots of a dataset's instrument scores for individual items, domains and totals (weighted and unweighted).

MUR 4) *Utility mapping model construction tools* that: (i) attach structured metadata about the target utility instrument and candidate predictor variables and covariates to a human records dataset; (ii) generate descriptive tables, a correlation matrix and plots about the variables to be assessed for inclusion in models; (iii) attach structured metadata about the candidate utility mapping models to be assessed; (iv) generate tabular and graphical summaries of the performance of each combination of model, predictors and covariates specified for evaluation by either a user or by a default algorithm; (v) strip confidential records from the constructed models so that they are able to be publicly shared.

MUR 5) *Utility mapping reporting tools* that: (i) generate from a reporting template a PDF catalogue summarising the predictive performance under multiple configurations of utility mapping models selected for public dissemination; (ii) generate from a reporting template (either a pre-written default or a user-supplied customisation) a scientific summary manuscript summarising a utility mapping study; (iii) share model catalogues and (if desired) scientific summary along with metadata about utility mapping models in an open access repository; and (iv) facilitate the authoring of a single consolidated study reproducibility program that implements all steps inclusive of data ingest, instrument scoring, model construction, report authoring and dissemination of study artefacts.

MUR 6) *Utility prediction tools* that: (i) search open access repositories for utility mapping models developed with readyforwhastnext; (ii) retrieve relevant metadata, including a link to the model catalogue for models specified by a user; (iii) applies selected utility mapping model to make out of sample predictions using a dataset provided by a user; and (iv) (where there is health utility data at two time points) convert predicted health utility scores to Quality Adjusted Life Years (QALYs).

## Model implementation

### Online service configuration
We established and configured accounts with the online services supported by ready4. We created a GitHub organisation (a collection of code repositories) where source code that we author is stored and version controlled at https://github.com/ready4-dev/. We configured individual repositories in our GitHub organisation to implement continuous integration to assess the compliance of our module libraries with policies specified by the Comprehensive R Archive Network (CRAN) [@CRAN2022]. <!-- To track our code coverage, we linked our GitHub organisation to an account we established at codecov [@codecov_2022].  --> To facilitate the creation and hosting of module library websites, we enabled GitHub Pages in each code repository. We also created a Zenodo community, a collection of permanent, uniquely identified repositories, at https://zenodo.org/communities/ready4/. We then linked our Zenodo community and GitHub organisation so that every time we specify a version of code in one of our GitHub repositories as a “release”, a copy of that code is automatically archived on Zenodo with a DOI. Finally, to manage model datasets, we created a dedicated collection (https://dataverse.harvard.edu/dataverse/ready4) within the Harvard Dataverse installation.

<!-- To track our code coverage, we linked our GitHub organisation to an account we established at codecov [@codecov_2022].  -->
<!-- The framework also supports integrations with the open science repositories Zenodo [@Zenodo2013] and Dataverse [@Dataverse2007] that provide persistent storage solutions that generate a Digital Object Identifier (DOI) for each code and data collection. -->
<!-- The third party services that our framework is designed to work with include GitHub, Zenodo, Dataverse, -->
<!-- codecov [@codecov_2022] -->

### Outputs
We have previously described a study [@Hamilton2021.07.07.21260129] to develop utility mapping models for use in samples of young people presenting to primary mental health services. The ready4 software framework was used in that study to develop CHEM modules, supply those modules with data and implement modelling analyses, creating the following artefacts:

@@

```{r, child = child_docs_ls$threeb, echo=FALSE}
```

(Table \@ref(tab:rfwnlibs)).

## Documentation website
We used functions from our foundation framework library to partially automate website updates relating to available CHEM modules, datasets and analysis programs.

## Transferability assessment
We created a checklist (Table \@ref(tab:checktb)) that we used to subjectively assess these study outputs against <!-- Edit_start -->explicit criteria for assessing transparent, reusable and updatable CHEMs that we have previously developed (add REF) <!-- Edit_end -->. For each criterion, we provided a global assessment of whether it was met using the responses “yes”, “no” or “partial”.  We believe our utility mapping study CHEMs have satisfactorily met five of the six criteria (T1, T2, R1, R2 and U1) and have partially met one criterion (U2). The main shortcomings that we identified when applying the assessment criteria was that we have yet to adequately implement unit testing of the R libraries authored as part of this study.

### 2024-02-23 Markdown/Manuscript/Child_RMDs/MS_Imp_Motivation.Rmd
nearly done on model

## Transferability
Although we are principally interested in using readyforwhatsnext to answer policy questions relating to the mental health of young people in Australia, we want to facilitate model transfer to other jurisdictions. The transferability requirements we have specified for readyforwhatsnext are to meet six explicit criteria for transparency, reusability and updatability. We have describe these criteria and their relationship to ethical modelling practice elsewhere [@ethicsCHEMS2024], but briefly they are:

@@

T3) Programming practices promote selective reuse;

T4) Licenses permit derivative works; <!-- rephrase Liceses permit derivative works-->

T5) Maintenance infrastructure is in place; and

T6) Systematic retesting and deprecation.

The readyforwhatsnext model is being derived from and applied to real Australian data (which can be empirical, simulated or assumption, so long as it is appropriate for use in analysis intended to inform decision-making). To help demonstrate the potential transferability of readyforwhatsnext to other decision contexts, we are also creating toy datasets. Toy data created for illustration purposes will be prominently labelled as not for use in decision-analysis.

A high level schematic guiding our implementation of readyforwhatsnext as a modular and open source CHEM is outlined in Figure \@ref(fig:fig1).

>>>>

## Transferability
We are principally interested in using readyforwhatsnext to answer policy questions relating to the mental health of young people in Australia. Australian mental health services are primarily planned and commissioned by the Australian Government, the governments of Australia's state and territories and independent organisations focused on smaller regions called Primary Health Networks. Promoting mentally healthy local communities is also an important role for Australian local governments. Australia is an international leader in developing innovative youth mental health service models that are subsequently adopted in other jurisdictions [@RN27]. For these reasons, we want readyforwhatsnext to be implemented in a manner that facilitates its transfer to multiple decision contexts.

However, there are ethical risks associated with each potential transfer, in particular the need to ensure social acceptability, fitness for purpose and appropriate use of readyforwhatsnext in each new decision context. For that reason, we have set the goal of readyforwhatsnext meeting six explicit criteria for transparency, reusability and updatability (TRU criteria). We have describe these criteria and their origins in ethical modelling practice elsewhere [@ethicsCHEMS2024], but briefly they are:

<!-- Model mutipurpose and complexity increasing validation [@Feenstra2022] -->

@@

R1) Programming practices promote selective reuse;

R2) Licenses permit derivative works; <!-- rephrase Liceses permit derivative works-->

U1) Maintenance infrastructure is in place; and

U6) Systematic retesting and deprecation.

We are developing readyforwhatsnext using real Australian data (which can be empirical, simulated or assumption, so long as it is appropriate for use in analysis intended to inform decision-making). To help demonstrate the potential transferability of readyforwhatsnext to other decision contexts, we are also creating toy datasets. Toy data created for illustration purposes is prominently labelled as not for use in decision-analysis.
<!-- PHNS -->
A high level schematic guiding our implementation of readyforwhatsnext as a transferable CHEM is outlined in Figure \@ref(fig:fig1).

### 2024-02-23 Markdown/Manuscript/Child_RMDs/MS_Imp_Toolkit.Rmd
nearly done on model

We began developing a prototype software framework in order to address a number of challenges we encountered during the planning and early implementation of readyforwhatsnext. The software framework is called ready4.

## User requirements
We created ready4 with one primary user group in mind - ourselves. The user requirements (URs) for ready4 evolved over six years (2018-2024) as we became aware of new issues that we needed to solve. Currently, these requirements are:

UR 1) A *template module* for use in CHEM implementations in which modules can: (i) be run as independent models; (ii) safely combined, sharing inputs and outputs with each other without unintended interference; and (iii) be selectively replaced, updated or extended.

UR 2) *Developer tools* that integrate with online open source software development services to support streamlined workflows for authoring R libaries of CHEM modules that are: (i) created using the template module; (ii) written in a consistent house style; (iii) consistently documented; (iv) licensed for reuse; (v) bundled with citation data specifying authorship, funding source, version number and a Digital Object Identifier (DOI); and (vi) quality assured with publicly available acceptance and unit tests.

UR 3) A *programming syntax* that promotes simplicity and consistency in how algorithms associated with CHEM modules are described and used in health economic analysis programs.

<!-- UR 4) Integration with online open source software development services to streamline the *authoring, testing, documenting and sharing of CHEM modules*.  -->

UR 5) *Data management tools* that integrate with online data repository services to streamline the ingesting, labeling and sharing of publicly available and confidential data.

UR 6) *Reporting tools* that: (i) help author programs for generating analysis reports and scientific summaries from a template that can render documents in HTML, Adobe PDF and Microsoft Word file formats; (ii) retrieve version specific reporting template programs from online code repositories and (iii) supply study specific data (e.g authorship details, input data and analysis results) to reporting template programs to render reports and scientific summaries.
<!-- help generate tables for multiple outputs, retrieve templates, modify templates with authorship and results -->

UR 7) *Search tools* to retrieve web based information on a CHEM project's: (i) publicly available model modules, module libraries and tutorials; (ii) datasets and data collections; and (iii) replication programs and reporting templates.

UR 8) *Documentation tools* that integrate with open source website development and hosting infrastructure to help: (i) develop a consolidated project documentation website that synthesises data from mulitple code library websites and code and data repositories; and (ii) partially automate the updating of website resources such as tutorials and code and data release information.

## Implementation
<!-- The software framework aims to provide a toolkit for: (i) enabling modular implementation of CHEMs; (ii) authoring and documenting CHEM modules; (iii) managing the labelling and transfer of CHEM input and output data; and (iv) authoring reproducible analyses that apply CHEMs to compatible data. -->
We implemented the software framework as R [@RCORE2022] code libraries that integrate with a number of online services and which are supported by a documentation website.

@@

One library provides the foundation for the ready4 framework. <!-- In modular model implementations, modules need to be able to share inputs and outputs with each other and to be run as independent models [@barros2023empowering].  -->The ready4 foundation library defines a template CHEM module using R’s S4 class system, that supports an object-oriented programming paradigm. Two notable features of object-oriented programming are encapsulation [@8717448] and inheritence [@8717448]. Encapsulation allows a CHEM module to bundle model data and algorithms in a protected environment. Encapsulation can be used to help ensure that CHEM modules continue to work as intended when they are combined<!-- [@ready4oop2022] -->. Inheritence allows new CHEM modules to be created that inherit some or all of the properties of a parent module. Inheritence is useful in cases where it is necessary to update CHEM modules that are being combined to account for interaction effects. Inheritance also facilitates the selective editing of CHEM modules when transferring models to different decision contexts<!-- [@ready4oop2022] -->. The ready4 template CHEM module can therefore be used to create other CHEM modules that inherit common set of properties (meeting *UR 1*). One of these inherited properties is a novel syntax of 15 core commands that enable CHEM module algorithms to be consistently named (meeting *UR 3*). The foundation library also contains tools for retrieving web-based information on CHEM modules, datasets and analysis programs authored with ready4 (meeting *UR 7*) and tools for developing and maintaining a project documentation website (*UR 8*).

Three framework libraries are designed to meet *URs 2 and 4*. <!-- Define functional and object-oriented approaches, acceptance and unit testing. -->The R language supports functional and object-oriented programming paradigms [@10.1214/13-STS452]. Authoring with each of these paradigms is facilitated by a dedicated CHEM module authoring library. One module authoring library contains tools for writing functions in a consistent house style and automatically generating basic documentation for each function. A second module authoring library contains tools to help streamline and standardise the authoring of novel, documented CHEM modules from the template CHEM module. A third module authoring library provides tools for disseminating themed bundles of CHEM modules as R libraries that are:

-	documented (with a website and PDF manuals);

-	licensed (using the copyleft GNU GPL-3 [66] by default);

-	easily citable (citation information can be retrieved within an R session or from hosting repositories); and

-	quality assured (each update triggers continuous integration workflows, including any acceptance and unit tests created by module library authors).

A library for managing CHEM data contains tools for supplying CHEM modules with input data ingested from local (i.e., a user's computer) or remote (online repositories) locations, labelling CHEM module datasets and exporting CHEM module data to online repositories (meeting *UR 5*). A library for authoring reproducible analysis programs and reporting subroutines (*UR6*) contains tools to help write executables that apply CHEM modules to compatible datasets for the purpose of undertaking health economic analyses. The library supports the creation of analysis programs that are self-documenting (code is integrated with plain English explanations of what it does) and subroutines that can be used as templates that trigger the creation of explanatory documents (e.g., a scientific manuscript).

@@

###	Online services 
Framework libraries are designed to be used in conjunction with a number of third-party online services that users of ready4 will need to establish and configure accounts with. The framework's developer tools integrate with online code development, testing and archiving services. The ready4 framework uses the GitHub [@github2007] service's tools for: software development, testing, version control and distribution; hosting of documentation websites; and transparent record keeping of collaborator contributions. A useful concept for informing software users about the extensiveness of testing procedures is code coverage [@ERICWONG2010188] - the proportion of code that has been explicitly tested. The ready4 framework uses the codecov [@codecov_2022] service to measure and share information about code coverage. The open science repository service Zenodo [@Zenodo2013] is used to provide persistent storage, uniquely identified with a a Digital Object Identifier (DOI), of each code release.

The framework's data management tools use the Dataverse [@Dataverse2007] data repository service for persistent, uniquely identifiable and versioned storage of model input and output data. For the management of frequently updated datasets that do not require persistent storage, ready4 uses GitHub.

###	Documentation website
We developed a framework documentation website (https://www.ready4-dev.com) that provides guidance to model developers on how to use and contribute improvements to the ready4 software framework and CHEM modules developed with it. The documentation website is versioned, which means documentation relating to prior versions of framework software can be archived, retrieved and viewed. The documentation website was developed using the Hugo framework [@hugo_2023], Docsy theme [@docsy_2023] and Algolia DocSearch [@algoliadocsearch_2023] and is hosted using the Netlify [@netlify_2023] service.  We linked our Netlify account to our GitHub organisation so that the project website would automatically update whenever its source code (publicly available in a GitHub repository) was edited.

>>>>

To enable us to adopt a development approach to readyforwhatsnext that is consistent with meeting all six TRU criteria, we developed a prototype software framework. The software framework is called ready4.

## Framework user requirements
We created ready4 with one primary user group in mind - ourselves. The framework user requirements (FURs) for ready4 evolved over six years (2018-2024) as we became aware of new issues that we needed to solve. Currently, these requirements are:

FUR 1) A *template module* for use in CHEM implementations in which modules can: (i) be run as independent models; (ii) safely combined, sharing inputs and outputs with each other without unintended interference; and (iii) be selectively replaced, updated or extended.

FUR 2) A *programming syntax* that promotes simplicity and consistency in how algorithms associated with CHEM modules are described and used in health economic analysis programs.

FUR 3) *Developer tools* that integrate with online software development services to support streamlined workflows for authoring R libaries of CHEM modules that are: (i) created using the template module; (ii) written in a consistent house style; (iii) consistently documented; (iv) licensed for reuse; (v) bundled with citation data specifying authorship, funding source, version number and a Digital Object Identifier (DOI); and (vi) quality assured with publicly available acceptance and unit tests.

<!-- FUR 4) Integration with online open source software development services to streamline the *authoring, testing, documenting and sharing of CHEM modules*.  -->

FUR 4) *Data management tools* that integrate with online data repository services to streamline the ingesting, labeling and sharing of publicly available and confidential data.

FUR 5) *Reporting tools* that: (i) help author reporting template programs that render documents in HTML, Adobe PDF and Microsoft Word file formats; (ii) retrieve version specific reporting template programs from online code repositories and (iii) supply study specific data (e.g authorship details, input data and analysis results) to reporting template programs to render reports and scientific summaries.
<!-- help generate tables for multiple outputs, retrieve templates, modify templates with authorship and results -->

FUR 6) *Search tools* to retrieve web based information on a CHEM project's: (i) publicly available model modules, module libraries and tutorials; (ii) datasets and data collections; and (iii) replication programs and reporting templates.

FUR 7) *Documentation tools* that integrate with open source website development and hosting infrastructure to help: (i) develop a consolidated project documentation website that synthesises content from the individual websites of the project's module libraries, datasets and programs; and (ii) partially automate the updating of website resources such as tutorials and itemised lists of code and data releases.

## Framework implementation
<!-- The software framework aims to provide a toolkit for: (i) enabling modular implementation of CHEMs; (ii) authoring and documenting CHEM modules; (iii) managing the labelling and transfer of CHEM input and output data; and (iv) authoring reproducible analyses that apply CHEMs to compatible data. -->
We implemented ready4 as R [@RCORE2022] code libraries that integrate with a number of online services. The framework is documented by a project website.

@@

One library provides the foundation for the ready4 framework. <!-- In modular model implementations, modules need to be able to share inputs and outputs with each other and to be run as independent models [@barros2023empowering].  -->The ready4 foundation library defines a template CHEM module using R’s S4 class system, that supports an object-oriented programming paradigm. Two notable features of object-oriented programming are encapsulation [@8717448] and inheritence [@8717448]. Encapsulation allows a CHEM module to bundle model data and algorithms in a protected environment, which is useful for helping ensure that CHEM modules continue to work as intended when they are combined<!-- [@ready4oop2022] -->. Inheritence allows new CHEM modules to be created that inherit some or all of the properties of a parent module. Inheritence is useful in cases where it is necessary to update CHEM modules that are being combined to account for interaction effects or to selective edit CHEM modulesbeing transfered to different decision contexts<!-- [@ready4oop2022] -->. The ready4 template CHEM module can be used to create other CHEM modules that inherit a common set of properties (meeting *FUR 1*). One of these inherited properties is a novel syntax of 15 core commands that enable CHEM module algorithms to be consistently named (meeting *FUR 2*). The foundation library also contains tools for retrieving web-based information on CHEM modules, datasets and analysis programs authored with ready4 (meeting *FUR 6*) and tools for developing and maintaining a project documentation website (*FUR 7*).

Three framework module authoring libraries are designed to meet *FUR 3*. <!-- Define functional and object-oriented approaches, acceptance and unit testing. -->The R language supports functional and object-oriented programming paradigms [@10.1214/13-STS452]. Authoring with each of these paradigms is supported by ready4. One module authoring library contains tools for writing functions in a consistent house style and automatically generating basic documentation for each function. A second module authoring library contains tools to help streamline and standardise the authoring of novel, documented CHEM modules from the template CHEM module. A third module authoring library provides tools for disseminating themed bundles of CHEM modules as R libraries that are: documented (with a website and PDF manuals); licensed (using the copyleft GNU GPL-3 [66] by default); easily citable (citation information can be retrieved within an R session or from hosting repositories); and quality assured (each update triggers continuous integration workflows, including any acceptance and unit tests created by module library authors).

A library for managing CHEM data contains tools for supplying CHEM modules with input data ingested from local (i.e., a user's computer) or remote (online repositories) locations, labelling CHEM module datasets and exporting CHEM module data to online repositories (meeting *FUR 4*). A library for authoring reproducible analysis programs and reporting subroutines (*FUR5*) contains tools to help write executables that apply CHEM modules to compatible datasets for the purpose of undertaking health economic analyses. The library supports the creation of analysis programs that are self-documenting (code is integrated with plain English explanations of what it does) and subroutines that can be used as templates that trigger the creation of explanatory documents (e.g., a scientific manuscript).

@@

###	Online services 
Framework libraries are designed to be used in conjunction with a number of third-party online services that users of ready4 will need to establish and configure accounts with. The framework's developer tools integrate with online code development, testing and archiving services. The ready4 framework uses the GitHub [@github2007] service's tools for: software development, testing, version control and distribution; hosting of documentation websites; and transparent record keeping of collaborator contributions. The continuous integration [@CI2017] tools provided by GitHub are used to trigger systematic retesting of module libraries with every edit. <!-- Imported -->These tests can be unit tests (to verify that small, isolated sections of code produce the correct output when run independently) and acceptance tests (to verify that the correct output is produced when multiple code components are run together to perform tasks that meet core user-requirements [@martin2003agile]). A useful concept for informing software users about the extensiveness of testing procedures is code coverage [@ERICWONG2010188] - reports of the proportion of code that has been explicitly tested. The ready4 framework uses the codecov [@codecov_2022] service to measure and share information about code coverage. <!-- End_Imported -->The open science repository service Zenodo [@Zenodo2013] is used to provide persistent storage, uniquely identified with a a Digital Object Identifier (DOI), of each code release. The framework's data management tools use the Dataverse [@Dataverse2007] data repository service for persistent, uniquely identifiable and versioned storage of model input and output data. For the management of frequently updated datasets that do not require persistent storage, ready4 uses GitHub.

###	Documentation website
A project documentation website (https://www.ready4-dev.com) provides guidance to model developers on how to use and contribute improvements to the ready4 software framework. The documentation website is versioned, which means documentation relating to prior versions of framework software can be archived, retrieved and viewed. The documentation website was developed using the Hugo framework [@hugo_2023], Docsy theme [@docsy_2023] and Algolia DocSearch [@algoliadocsearch_2023] and is hosted using the Netlify [@netlify_2023] service. We linked our Netlify account to our GitHub organisation so that the project website would automatically update whenever its source code (publicly available in a GitHub repository) was edited.

### 2024-02-23 Markdown/Manuscript/Child_RMDs/MS_Intro_Short.Rmd
nearly done on model

<!-- Imported_from_Ethics-->Key concerns for health economists when considering whether to reuse a model are generalisability (application without adaptation) and transferability (selective reuse and/or modification of model components) [@RN39]. <!-- End_Imported_from_Ethics -->A potential strategy for achieving both these goals is to make computational health economic models (CHEMs) both modular and open-source. A modular model is constructed from multiple reusable and replaceable sub-models (modules) [@pan2021modular]. Modules can share inputs and outputs with other modules or can be run as independent models [@barros2023empowering]. Advantages of modular models include feasibility (large projects are broken into smaller tasks, with each component independently developed and tested) and flexibility (making it easier to selectively replace or update specific parts of a model and to scale up or down the level of granularity) [@pan2021modular]. Modular approaches are currently being used to facilitate the development of complex computational models in disciplines such as biology [@pan2021modular], ecology [@barros2023empowering] and neuroscience [@frazier2022robust]. In health economics the related and enabling concept of reference models has been recommended [@Afzali2013], but peer reviewed studies describing modular health economic models remain relatively rare, though examples exist in infectious disease [@Trauer2017] and cardiology [@Urach2013].

Modular CHEMs provide an opportunity for multiple modelling teams to contribute to, test and reuse models. To enhance this capacity, modular CHEMs may be implemented as open source projects that give others liberal permissions to access and use model source code and data [@pan2021modular; @barros2023empowering; @frazier2022robust]. Although there appears to be in principle support from many health economists for greater use of open source CHEMs  [@Pouwels2022], actual implementations are rare [@Emerson2019; @Michalczyk2018; @Feenstra2022]. Barriers to adoption of open source CHEMs include concerns about intellectual property, confidentiality, model misuse and the resources required to support open source implementations [@Pouwels2022; @Wu2019]. <!-- Adherence to good practice guidance is an essential requirement for healthcare modelling [@Erdemir2020], but  --><!-- Guidelines for implementing open source CHEMs remain scarce, piecemeal and need improving [@Sampson2019].  -->As many health economic models are owned by pharmaceutical companies and consultancies, commercial considerations can limit the reuse of models and their constituent code and data [@Feenstra2022]. Legal and ethical issues such as privacy and confidentiality requirements further limit public release of some model artefacts [@Pouwels2022].

@@

Some of the barriers<!-- Give examples --> to the development of open-source and modular CHEMs may be amenable to technical solutions such as software frameworks.<!-- Check last sentence was not used in ethics manuscript  --> A software framework is a shared common technology used by developers to collaboratively author software and which is not typically visible to software end-users [@myllarniemi2018development]. A software framework provides a foundation for developing multiple software applications with shared resources (e.g., code and data files), that can be modified to suit specific needs. Advantages of using software frameworks include facilitating code reuse and extension, promoting good programming practice and the capability to provide enhanced functionality and performance without additional effort by developers [@edwin2014software]. Software frameworks have widely been developed and implemented in data science, for example, PyTorch [@PyTorch2019] for machine learning using Python. However, software frameworks can be challenging and time consuming to create and may become excessively complex over time [@edwin2014software]. Software frameworks can also be difficult to learn, often requiring model developers to undergo specialist training [@myllarniemi2018development].

>>>>

<!-- Imported_from_Ethics-->Key concerns for health economists when considering whether to reuse a model are generalisability (application without adaptation) and transferability (selective reuse and/or modification of model components) [@RN39]. Health economic models are likely to require at least some modification before they can be validly applied to a new jurisdiction, time period or decision problem. The difficulty of undertaking such a model transfer depends in part on whether the Computational Health Economic Model (CHEM) - the software files that implement the model - can be readily understood, used and edited.

<!-- End_Imported_from_Ethics -->A potential strategy for implementing transferable CHEMs is to adopt a modular and open-source approach to model development. A modular model is constructed from multiple reusable and replaceable sub-models (modules) [@pan2021modular]. Modules can share inputs and outputs with other modules or can be run as independent models [@barros2023empowering]. Advantages of modular models include feasibility (large projects are broken into smaller tasks, with each component independently developed and tested) and flexibility (making it easier to selectively replace or update specific parts of a model and to scale up or down the level of granularity) [@pan2021modular]. Modular approaches have been used to facilitate the development of complex computational models in disciplines such as biology [@pan2021modular], ecology [@barros2023empowering] and neuroscience [@frazier2022robust]. In health economics the related and enabling concept of reference models has been recommended [@Afzali2013]. Peer reviewed studies describing modular health economic models remain relatively rare, though examples exist in infectious disease [@Trauer2017] and cardiology [@Urach2013].

<!-- Modular CHEMs provide an opportunity for multiple modelling teams to contribute to, test and reuse models.  -->
A number of modular modelling projects have been implemented as open source projects that give others liberal permissions to access and use model source code and data [@pan2021modular; @barros2023empowering; @frazier2022robust]. Many health economists support greater use of open-source CHEMs as a means of improving model transparency, promoting model reuse, making model development more efficient and gaining the confidence of model users [@Pouwels2022]. However, actual implementations of open-source CHEMs are rare [@Emerson2019; @Michalczyk2018; @Feenstra2022], with barriers to adoption including concerns about intellectual property, confidentiality, model misuse and the resources required to maintain open source implementations [@Pouwels2022; @Wu2019]. <!--Benefits --><!-- Adherence to good practice guidance is an essential requirement for healthcare modelling [@Erdemir2020], but  --><!-- Guidelines for implementing open source CHEMs remain scarce, piecemeal and need improving [@Sampson2019].  -->Health economic models can be owned by pharmaceutical companies and consultancies, so commercial considerations can limit the reuse of models and their constituent code and data [@Feenstra2022]. Barriers relating to model generalisability and transferability and the software platforms used to implement CHEMs are also important [@Pouwels2022].

@@

Some of the technical barriers<!-- Give examples --> to the development of transferable CHEMs could be addressed by appropriate software frameworks.<!-- Check last sentence was not used in ethics manuscript  --> A software framework is a shared common technology used by developers to collaboratively author software and which is not typically visible to software end-users [@myllarniemi2018development]. A software framework provides a foundation for developing multiple software applications with shared resources (e.g., code and data files), that can be modified to suit specific needs. Advantages of using software frameworks include facilitating code reuse and extension, promoting good programming practice and the capability to provide enhanced functionality and performance without additional effort by developers [@edwin2014software]. Software frameworks have widely been developed and implemented in data science, for example, PyTorch [@PyTorch2019] for machine learning using Python. However, software frameworks can be challenging and time consuming to create and may become excessively complex over time [@edwin2014software]. Software frameworks can also be difficult to learn, often requiring model developers to undergo specialist training [@myllarniemi2018development].

### 2024-02-23 Markdown/Manuscript/Child_RMDs/MS_Tables.Rmd
nearly done on model

```{r echo=FALSE}
if(params$X@tables_in_body_lgl){
  child_docs_ls <- list(one = "../Child_RMDs/MS_Tables_1.Rmd",
                        two = "../Child_RMDs/MS_Tables_2.Rmd",
                        three = "../Child_RMDs/MS_Tables_3.Rmd",
                        four = "../Child_RMDs/MS_Tables_4.Rmd")
}else{
    child_docs_ls <- list(one = NULL,
                          two = NULL,
                          three = NULL,
                          four = NULL)
}
```

>>>>

```{r echo=FALSE}
if(params$X@tables_in_body_lgl){
  child_docs_ls <- list(
    one = NULL,
    # "../Child_RMDs/MS_Tables_1.Rmd",
                        two = NULL,
    # "../Child_RMDs/MS_Tables_2.Rmd",
                        three = "../Child_RMDs/MS_Tables_3.Rmd",
    threeb = "../Child_RMDs/MS_Tables_3b.Rmd", 
                        four = "../Child_RMDs/MS_Tables_4.Rmd")
}else{
    child_docs_ls <- list(one = NULL,
                          two = NULL,
                          three = NULL,
                          threeb = NULL,
                          four = NULL)
}
```
